Security on Networks

### 2013-05-16 paper/paper.tex
a

As epidemics spread on computer, disease propagation, and financial networks, agents in the network often undertake costly investments in security to protect themselves from infection. However, these investments are often imperfect and typically succeed with some probability less than one. Furthermore, the cost of a security investment and its probability of success both increase with the chosen level of security. Thus agents face a tradeoff between choosing high investment in security to minimize infection probability and choosing low investment to minimize cost. Given the easily definable utility functions of agents, it is appropriate to model the choice of security as a game on a network.

@@

@@

\subsection{Dynamic Simulation Results}

@@

>>>>

As epidemics spread on computer, epidemiological, and financial networks, agents in the network often undertake costly investments in security to protect themselves from infection. However, these investments are often imperfect and typically succeed with some probability less than one. Furthermore, the cost of a security investment and its probability of success both increase with the chosen level of security. Thus agents face a tradeoff between choosing high investment in security to minimize infection probability and choosing low investment to minimize cost. Given the easily definable utility functions of agents, it is appropriate to model the choice of security as a game on a network.

@@

\subsection{Dynamic Infection Model}

@@

We consider the real-world application of the spread of HIV in sub-Saharan Africa. We choose to use the prevalence of HIV as the attack probability, as a measure of the invasiveness of HIV. We use the probability of death from HIV as the cure probability; because there is no current actual cure for HIV, we choose the probability of death as a measure of how often an infected node is removed from the graph. From online HIV statistics, we decide to use $\alpha=0.05$ and $\gamma=0.06$, with a preferential attachment model, and a scope of $1$. Simulations were run for different attack and cure probabilities for either an Erdos-Reyni graph with $n=100$ and $p=0.05$, or a preferential attachment model with $n=100$ and $k=5$. We assume a scope of $1$.

@@

\section{Acknowl
